An SMT-based Approach to Coverability Analysis

### 2014-02-05 paper/workspace/main.tex
Added results for methods invariant and invariant with minimization

  - Property: Process 1 and Process 2 are never in their respective critical section at the same time.

  - Property: p3 + q5 <= 1

@@

  - Negated Property \neg P:

    p3 + q5 >= 2
\end{verbatim}

@@

@@

@@

    a        <  2 * target_1

    a        >= target_1
    b        >= target_1
    nbit2    >= 0
    target_1 >= 0

@@

    a        = 1
    b        = 1
    nbit2    = 1
    target_1 = 1

@@

    a + b + nbit2 <= 1

@@

    a     > 0 => b_a     = 1
    |            -----------
    |               |
    |            place appears in invariant
    |
    place coefficient in the invariant

    a     = 0 => b_a     = 0
    |           ------------
    |               |
    |            place does not appear in invariant
    |
    place coefficient in the invariant

    b     > 0 => b_b     = 1
    b     = 0 => b_b     = 0
    nbit2 > 0 => b_nbit2 = 1
    nbit2 = 0 => b_nbit2 = 0

    b_a + b_b + b_nbit2 < 3
    -------------------   |
                |         |
                |    number of places appearing in current invariant for A'
                |    = #{s | A'(s) > 0} = #{a, b, nbit2}
                |
  number of places appearing in new invariant

@@

    a        = 1
    b        = 1
    nbit2    = 0
    target_1 = 1

@@

    a + b <= 1
\end{verbatim}

@@

>>>>

  - Property 1: Process 1 and Process 2 are never in their respective critical section at the same time.

  - Property 1: p3 + q5 <= 1

  - Property 2: Process 1 is in at most one state at a time

  - Property 2: p1 + p2 + p3 <= 1

@@

  - Using property 2

  - Negated property 2 \neg P:

    p1 + p2 + p3 >= 2
\end{verbatim}

@@

  - Using property 1

  - Negated property 1 \neg P:

    p3 + q5 >= 2

@@

  - Using property 2

@@

    0 >= - p1 + p2      + bit1 - nbit2
    0 >=      - p2 + p3
    0 >= + p1      - p3 - bit1 + nbit2

    0 >= - q1 + q2                - nbit2
    0 >=      - q2 + q3
    0 >=           - q3 + q4      + nbit2
    0 >= + q1           - q4
    0 >=      - q2           + q5
    0 >= + q1                - q5 + nbit2

    p1 + q1 + nb1 + nb2 < 2 * target_1

    p1    >= target_1
    p2    >= target_1
    p3    >= target_1
    bit1  >= 0
    nbit1 >= 0
    q1    >= 0
    q2    >= 0
    q3    >= 0
    q4    >= 0
    q5    >= 0
    nbit2 >= 0

    target_1 >= 0

@@

    p1       = 3
    p2       = 2
    p3       = 2
    bit1     = 1
    nbit1    = 0
    q1       = 0
    q2       = 0
    q3       = 0
    q4       = 0
    q5       = 0
    nbit2    = 0
    target_1 = 2

@@

    3 * p1 + 2 * p2 + 2 * p3 + bit1 <= 3

@@

    p1     > 0 => b_p1   = 1
    |            -----------
    |               |
    |            place p1 appears in invariant
    |
    place p1 coefficient in the invariant

    p1     = 0 => b_p1   = 0
    |           ------------
    |               |
    |            place p1 does not appear in invariant
    |
    place p1 coefficient in the invariant

    p2    > 0 => b_p2    = 1
    p2    = 0 => b_p2    = 0
    p3    > 0 => b_p3    = 1
    p3    = 0 => b_p3    = 0
    bit1  > 0 => b_bit1  = 1
    bit1  = 0 => b_bit1  = 0
    nbit1 > 0 => b_nbit1 = 1
    nbit1 = 0 => b_nbit1 = 0

    q1    > 0 => b_q1    = 1
    q1    = 0 => b_q1    = 0
    q2    > 0 => b_q2    = 1
    q2    = 0 => b_q2    = 0
    q3    > 0 => b_q3    = 1
    q3    = 0 => b_q3    = 0
    nbit2 > 0 => b_nbit2 = 1
    nbit2 = 0 => b_nbit2 = 0

    b_p1 + b_p2 + b_p3 + b_bit1 + b_nbit1 + b_q1 + b_q2 + b_q3 + b_q4 + b_q5
         + b_nbit2 < 4
    --------------   |
                |    |
                |    number of places appearing in current invariant for A'
                |    = #{s | A'(s) > 0} = #{p1, p2, p3, bit1}
                |
  number of places appearing in new invariant

@@

    p1       = 1
    p2       = 1
    p3       = 1
    bit1     = 0
    nbit1    = 0
    q1       = 0
    q2       = 0
    q3       = 0
    q4       = 0
    q5       = 0
    nbit2    = 0
    target_1 = 1

@@

    p1 + p2 + p3 <= 1
\end{verbatim}

@@

  - Using property 1
